Decoding Toronto's Crime Patterns: A Comprehensive Analysis of Victims and Trends (2014-2022)

### 2024-01-23 Toronto_Victims_of_Crimes/outputs/paper/paper.qmd
final update paper files

This paper employs R (R Core Team 2020) to analyze a dataset sourced from opendatatoronto (Gelfand 2020), encompassing all identified victims of crimes against persons. This inclusive dataset considers cases that may have been deemed unfounded post-investigation, incidents occurring beyond the City of Toronto limits, or those lacking verified locations. The analysis extracts key variables such as report_year, subtype, age_group, and count\_, excluding age_cohort, sex, category, and assault_subtype. Omitted are unknown values for age_group, age_cohort, and sex, as they don't contribute explicitly to defining data groups. The dataset lacks explicit details regarding these unknown values. Additionally, the analysis focuses solely on the top three reported crimes---robbery, assault, and sexual violation. The exclusion of 'other' crimes in the cleaned_data set is attributed to its inherent uncertainty. Notably, the data within this paper centers on trends related to these three crimes, with age groups classified into three subgroups: adult, youth, and child. The overarching trend indicates a resurgence in reported victims of crimes following a period of decline, 2020 - 2021.

@@

# Install the necessary packages if not already installed
# install.packages(c("opendatatoronto", "knitr", "lubridate", "tidyverse", "kableExtra"))

@@

# Reference

>>>>

This paper employs R (R Core Team 2020) to analyze a dataset sourced from opendatatoronto (Gelfand 2020), encompassing all identified victims of crimes against persons. The dataset under analysis comprises observations on the number of victims reported each year for crimes, including robbery, assault, and sexual violation, to the Toronto Police from 2014 to 2022. This inclusive dataset considers cases that may have been deemed unfounded post-investigation, incidents occurring beyond the City of Toronto limits, or those lacking verified locations. The analysis extracts key variables such as report_year, subtype, age_group, and count\_, excluding age_cohort, sex, category, and assault_subtype. Omitted are unknown values for age_group, age_cohort, and sex, as they don't contribute explicitly to defining data groups. The dataset lacks explicit details regarding these unknown values. Additionally, the analysis focuses solely on the top three reported crimes---robbery, assault, and sexual violation. The exclusion of 'other' crimes in the cleaned_data set is attributed to its inherent uncertainty. Notably, the data within this paper centers on trends related to these three crimes, with age groups classified into three subgroups: adult, youth, and child. The overarching trend indicates a resurgence in reported victims of crimes following a period of decline, 2020 - 2021.

@@

# Install the necessary packages if not already installed
install.packages(c("opendatatoronto", "knitr", "lubridate", "tidyverse", "kableExtra"))

@@

# References
